Higher-Order unification for free!

### 2024-04-17 paper/main.tex
update th 6.4

\begin{proof}[Proof sketch]
  By the definition of \mapdeduplication, any two occurrencies of the same \Fo{} 
  variable used at different arities are compiled to two
  variables $A^m$ and $C^n$ related by a chain of \linketa.
  Whenever the two variables are assigned to the non-unifiable terms,
  the chain of \linketa is entirely waken up refining little by little
  the intermediate variables between $A^m$ and $C^n$ leading eventually to a failure. 
  On the other
  hand, if the two variables still remain unifiable after their assignement, 
  then the activation of 
  the corresponding \linketa just refines the chain, by reducing eventually
  its length.
\end{proof}
% \todo{Not sure I fullfy fixed the proof, but the old oen was not ok}

>>>>

\begin{proof}[Proof sketch]
  By the definition of \mapdeduplication, any two occurrencies of the same \Fo{} 
  variable used at different arities are compiled to two
  variables $A^m$ and $C^n$ related by a chain of \linketa.
  % Attenzione a questo caso:
  %    A =𝜂 λx.(B x)   e    x |- B x =𝜂 λx.(C x)           (from a map dedup, where A e C, sono stessa variabile con diff arities)
  %  se (C x) è instanziato a (f (D x)) allora non c'è nessun progress:
  %  il rhs del secondo link diventa (λx.(f (D x))) che è un maybe-eta
%
  Without loss of generality, we pose $m < n$. If $A^m$ is assigned to a term
  $\lambda \vec{x}.t$ with $q$ being the length of $\vec{x}$. If $t$ is a rigid
  term, then the chain of links between $A^m$ and $C^n$ is completely triggered
  so that $C^n$ is assigned to $\lambda \vec{x}.t$ $\eta$-expanded $n-m$ times.
  Note that in this case fidelity is guaranteed, since term unified to $C^n$
  sohuld also unify with $A^m$. Otherwise, if $t$ is a variable, the chain of
  links is shrinked by $q$. Note that if this length is bigger then $n-m$ again
  the full chain collapse and $A^m$ and $C^n$ are agian tiny coupled. Otherwise,
  if $q < n-m$, it means that $C^n$ can always be assigned to any term starting
  with at least $q$ lambdas. In this second case fidelity is also guaranteed,
  due to the constraint of the number of lambda by which $C^n$ should start.
%
  % not starting with $\lambda$, then the entrire chain of link is
  % immediately waken up, assigning $C^n$ to $x_1\dots x_{n-m} \vdash t \appsep
  % x_1\dots x_{n-m}$, which is the $t$ $\eta$-expanded $n-m$ times. Hence, $A^m$
  % and $C^n$ are tiny coupled. If $A^m$ is assigned to a term of the form
  % $\lambda \vec{x}.t$, then if $t$ is rigid, the chain of links between $A^m$
  % and $C^n$ completely triggered, is shrinked by the length of $\vec{x}$. Note
  % that if $t$ is rigid, by the previous sentence, the remi
%
  % If $A^m$ is instantiated, 
%
  % Whenever the two variables are assigned to the non-unifiable terms,
  % the chain of \linketa is entirely waken up refining little by little
  % the intermediate variables between $A^m$ and $C^n$ leading eventually to a failure. 
  % On the other
  % hand, if the two variables still remain unifiable after their assignement, 
  % then the activation of 
  % the corresponding \linketa just refines the chain, by reducing eventually
  % its length.
\end{proof}
% \todo{Not sure I fullfy fixed the proof, but the old oen was not ok}
